Active Learning for Level Set Estimation

### 2013-05-01 figurefactory/files/ev_bgape_eps.tex
Most of the changes discussed with Andreas

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-6pt},
ylabel shift={-4pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=2
]

>>>>

\begin{axis}[%
tick label style={font=\footnotesize},
label style={font=\footnotesize},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\footnotesize},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=2
]

### 2013-05-01 figurefactory/files/ev_chl_eps.tex
Most of the changes discussed with Andreas

@@

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-6pt},
ylabel shift={-4pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=1
]
color=blue,
mark size=1.3pt,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=red!88!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=red!92!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=red!96!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=red,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor1,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor2,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor3,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor4,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor5,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor6,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor7,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor8,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor9,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor10,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor11,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor12,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor13,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor14,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor15,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor16,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor17,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor18,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor19,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor20,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor21,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor22,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor23,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor24,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor25,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor26,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor27,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor28,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor29,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor30,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor31,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor32,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor33,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor34,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor35,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor36,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor37,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor38,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor39,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor40,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor41,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor42,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor43,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor44,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor45,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor46,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor47,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor48,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor49,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor50,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor51,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor52,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor53,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor54,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor55,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!88!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!80!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!68!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!60!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!52!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor56,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor57,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor58,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor59,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor60,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor61,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor62,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor63,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor64,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor65,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor66,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor67,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor68,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor69,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor70,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor71,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor72,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!96!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!92!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!84!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!76!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!72!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=blue!64!black,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor73,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor74,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=mycolor75,draw=black,line width=0.1pt},

@@

color=blue,
mark size=1.3pt,
mark options={solid,fill=red!84!black,draw=black,line width=0.1pt},

@@

\end{axis}
\end{tikzpicture}%

>>>>

\usetikzlibrary{shapes,arrows,fit,calc,positioning}

@@

\begin{axis}[%
tick label style={font=\normalsize},
label style={font=\normalsize},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\normalsize},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=400,
xlabel={Samples},
ymin=0.5, ymax=1,
ylabel={$F_1$-score},
name=plot1,
axis lines*=left,
colormap={mymap}{[1pt] rgb(0pt)=(0.5,0,0); rgb(8pt)=(1,0,0); rgb(24pt)=(1,1,0); rgb(40pt)=(0,1,1); rgb(56pt)=(0,0,1); rgb(63pt)=(0,0,0.5625)},
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.06, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
tickwidth=0.1cm,
colorbar/width=0.15cm,
point meta min=0,
point meta max=1
]
%
mark size=1.9pt,
mark options={fill=red!88!black,draw=red!88!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=red!88!black,draw=red!88!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=red!92!black,draw=red!92!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=red!96!black,draw=red!96!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=red,draw=red,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor1,draw=mycolor1,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor2,draw=mycolor2,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor3,draw=mycolor3,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor4,draw=mycolor4,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor5,draw=mycolor5,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor6,draw=mycolor6,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor7,draw=mycolor7,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor8,draw=mycolor8,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor9,draw=mycolor9,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor10,draw=mycolor10,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor11,draw=mycolor11,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor12,draw=mycolor12,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor13,draw=mycolor13,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor14,draw=mycolor14,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor15,draw=mycolor15,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor16,draw=mycolor16,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor17,draw=mycolor17,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor18,draw=mycolor18,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor19,draw=mycolor19,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor20,draw=mycolor20,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor21,draw=mycolor21,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor22,draw=mycolor22,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor23,draw=mycolor23,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor24,draw=mycolor24,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor25,draw=mycolor25,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor26,draw=mycolor26,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor27,draw=mycolor27,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor28,draw=mycolor28,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor29,draw=mycolor29,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor30,draw=mycolor30,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor31,draw=mycolor31,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor32,draw=mycolor32,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor33,draw=mycolor33,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor34,draw=mycolor34,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor35,draw=mycolor35,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor36,draw=mycolor36,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor37,draw=mycolor37,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor38,draw=mycolor38,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor39,draw=mycolor39,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor40,draw=mycolor40,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor41,draw=mycolor41,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor42,draw=mycolor42,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor43,draw=mycolor43,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor44,draw=mycolor44,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor45,draw=mycolor45,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor46,draw=mycolor46,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor47,draw=mycolor47,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor48,draw=mycolor48,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor49,draw=mycolor49,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor50,draw=mycolor50,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor51,draw=mycolor51,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor52,draw=mycolor52,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor53,draw=mycolor53,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor54,draw=mycolor54,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor55,draw=mycolor55,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue,draw=blue,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!88!black,draw=blue!88!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!80!black,draw=blue!80!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!68!black,draw=blue!68!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!60!black,draw=blue!60!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!52!black,draw=blue!52!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor56,draw=mycolor56,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor57,draw=mycolor57,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor58,draw=mycolor58,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor59,draw=mycolor59,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor60,draw=mycolor60,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor61,draw=mycolor61,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor62,draw=mycolor62,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor63,draw=mycolor63,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor64,draw=mycolor64,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor65,draw=mycolor65,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor66,draw=mycolor66,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor67,draw=mycolor67,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor68,draw=mycolor68,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor69,draw=mycolor69,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor70,draw=mycolor70,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor71,draw=mycolor71,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor72,draw=mycolor72,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!96!black,draw=blue!96!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!92!black,draw=blue!92!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!84!black,draw=blue!84!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!76!black,draw=blue!76!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!72!black,draw=blue!72!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=blue!64!black,draw=blue!64!black,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor73,draw=mycolor73,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor74,draw=mycolor74,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=mycolor75,draw=mycolor75,line width=0.05pt},

@@

%
mark size=1.9pt,
mark options={fill=red!84!black,draw=red!84!black,line width=0.05pt},

@@

\node at (axis cs:230, 0.57) [shape=circle,draw=black,line width=1.2pt,inner sep=0.2pt,anchor=west,minimum size=20pt] {\LARGE$\epsilon$};
\node at (axis cs:90, 0.6) [anchor=west,minimum size=16pt] {\large \emph{large}};
\node at (axis cs:390, 0.6) [anchor=east,minimum size=16pt] {\large \emph{small}};

\draw[<-,line width=1.2pt] (axis cs:90, 0.57) -- (axis cs:230, 0.57);
\draw[->,line width=1.2pt] (axis cs:258, 0.57) -- (axis cs:390, 0.57);

\end{axis}
\end{tikzpicture}%

### 2013-05-01 figurefactory/files/limno_bgape_cl.tex
Most of the changes discussed with Andreas

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

>>>>

\begin{axis}[%
tick label style={font=\footnotesize},
label style={font=\footnotesize},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\footnotesize},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
tickwidth=0.1cm,
clip=false
]

### 2013-05-01 figurefactory/files/limno_bgape_sc.tex
Most of the changes discussed with Andreas

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
unbounded coords=jump,
colormap/jet,
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.04, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
colorbar/width=0.15cm,
tickwidth=0.1cm,
point meta min=0.9,
point meta max=9.3
]

>>>>

\begin{axis}[%
tick label style={font=\footnotesize},
label style={font=\footnotesize},
xlabel shift={-10pt},
ylabel shift={-17pt},
legend style={font=\footnotesize},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=1478,
xtick={0, 400, 1000, 1400},
xlabel={Length (m)},
ymin=-18, ymax=0,
ytick={0, -4, -14, -18},
ylabel={Depth (m)},
name=plot1,
axis lines*=box,
unbounded coords=jump,
colormap/jet,
colorbar right,
colorbar style={
  tickwidth=0.03cm,
  at={(1.04, 0)},
  anchor=south east,
  yticklabel pos=right,
  yticklabel shift={-2pt}
},
colorbar/width=0.15cm,
tickwidth=0.1cm,
point meta min=0.9,
point meta max=9.3
]

### 2013-05-01 figurefactory/files/voned_0_0.tex
Most of the changes discussed with Andreas

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

@@

\addplot [
color=green!60!black,
densely dotted,
line width=1.0pt,
forget plot
]
coordinates{
 (1.5,-2)(1.5,2)
};

\addplot [
color=green!60!black,
only marks,
mark=*,
mark size=2.5pt,
line width=1.0pt,
forget plot
]
coordinates{
 (1.5,-2)
};

\addplot [
color=green!60!black,
only marks,
mark=x,
mark size=3.5pt,
line width=1.5pt,
forget plot
]
coordinates{
 (1.5,2)
};

>>>>

\begin{axis}[%
tick label style={font=\footnotesize},
label style={font=\footnotesize},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\footnotesize},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0cm,
]

@@

%\addplot [
%color=black,
%solid,
%line width=1.5pt,
%mark size=3pt,
%mark=-,
%forget plot
%]
%coordinates{
% (1.25,-1)(1.25,3)
%};
%
%\node at (axis cs:0.1, 1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)$};
%\draw[->,line width=1pt] (axis cs:0.29, 1.5) to[in=90,out=0] (axis cs:0.4, 1.1);
%
%\node at (axis cs:1.47, 1.5) [anchor=east,minimum size=20pt] {\large$Q_t(\*x)$};
%
%\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)+2\sigma_t(\*x)$};
%\draw[->,line width=1pt] (axis cs:0.55, 3.5) to[in=90,out=0] (axis cs:0.65, 3.1);
%\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)-2\sigma_t(\*x)$};
%\draw[->,line width=1pt] (axis cs:0.55, -1.5) to[in=270,out=0] (axis cs:0.65, -1.1);

### 2013-05-01 figurefactory/files/voned_0_2.tex
Most of the changes discussed with Andreas

%\node at (axis cs:1.47, 1.5) [anchor=east,minimum size=20pt] {\large$Q_t(\*x)$};
%
%\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)+2\sigma_t(\*x)$};
%\draw[->,line width=1pt] (axis cs:0.55, 3.5) to[in=90,out=0] (axis cs:0.65, 3.1);
%\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)-2\sigma_t(\*x)$};
%\draw[->,line width=1pt] (axis cs:0.55, -1.5) to[in=270,out=0] (axis cs:0.65, -1.1);

>>>>

%\node at (axis cs:1.47, 1.5) [anchor=east,minimum size=20pt] {\large$Q_t(\*x)$};

\node at (axis cs:0.1, 3.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)+\beta_t^{1/2}\sigma_t(\*x)$};
\draw[->,line width=1pt] (axis cs:0.65, 3.5) to[in=90,out=0] (axis cs:0.75, 3.1);
\node at (axis cs:0.1, -1.5) [anchor=west,minimum size=20pt] {\large$\mu_t(\*x)-\beta_t^{1/2}\sigma_t(\*x)$};
\draw[->,line width=1pt] (axis cs:0.65, -1.5) to[in=270,out=0] (axis cs:0.75, -1.1);

### 2013-05-01 figurefactory/files/voned_cl_41_imp_1.tex
Most of the changes discussed with Andreas

\begin{axis}[%
tick label style={font=\tiny},
label style={font=\tiny},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\tiny},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0.1cm,
]

>>>>

\begin{axis}[%
tick label style={font=\footnotesize},
label style={font=\footnotesize},
label shift={-4pt},
xlabel shift={-6pt},
legend style={font=\footnotesize},
view={0}{90},
width=\figurewidth,
height=\figureheight,
scale only axis,
xmin=0, xmax=2,
xtick={0, 0.5, 1, 1.5, 2},
ymin=-2, ymax=4,
tickwidth=0.1cm,
]
